Reasoning About a Machine with Local Capabilities

### 2018-05-07 toplas/paper.tex
Added some more text about the future region relations and in particular masks

>>>>

\begin{toplas}
  In the future world relations, we must remember all region names in order to
  keep them extensional which is why we need to use masks. It does, however, not
  matter what kind of region is used to mask as it is the region name we must
  retain. This is why we allow $\revoked$ regions to be replaced by other
  regions in the two future world relations. This may seem unnecessary as the
  future world relation allows new regions to be added, but in private future
  worlds, for technical reasons, we need to be able to reinstate old regions
  with the same region names as they had in a past world. Further, we do not
  want public future worlds to be able to prevent reinstation in private future
  worlds. Private future worlds cannot revoke $\perma$ regions, so we cannot
  allow public future worlds to us $\perma$ regions as a mask for a revoked
  region.
\end{toplas}
